---
title: "SS4864ASS3"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SS4864ASS3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SS4864ASS3)
```
There are three useful theories in this document including: 

1.Riemann integration
2.Trapezoid Rule
3.Simpson's Rule

How to run the package:
f is a function with a single argument x
range is a vector specifying the lower and upper end points of the range of integration (a and b)
n is the number of intervals for the Riemann approximation
return a single value which is the approximation to the integral in one of the three ways above

```{r}
#plot of my function with the target area shaded.
library(tidyverse)
a <- 1
b <- 10
n <- 1000
dx <- (b - a)/n

f <- function(x){x^2}

xlist <- c()
ylist <- c()
for (x in seq(a, b-dx, dx)){
    xlist <- c(xlist, c(x, x, x + dx, x + dx))
    ylist <- c(ylist, c(0,f(x), f(x+dx), 0))
}

df <- tibble(x = xlist, y = ylist)

df %>%
    ggplot(aes(x = x, y = y)) +
    geom_line(data = tibble(x = seq(a, b, .001), 
                            y = f(x)), colour = "blue", lwd = 1) +
    geom_polygon(fill = "blue", alpha = 0.4)

```
```{r}
# to compare the three methods
library(tidyverse)
n <- seq(1, 100, 1)
l <- length(n)
ri <- vector(length = l)
tr <- vector(length = l)
si <- vector(length = l)
f <- function(x){x^2}

for (i in 1:l) {
    ri[i] <- riemann(f, c(1, 10), n[i])
    tr[i] <- trapezoid(f, c(1, 10), n[i])
    si[i] <- simpsons(f, c(1, 10), n[i])
}

df <- tibble(n, ri, tr, si)

df %>%
    ggplot(aes(x = n)) +
    geom_line((aes(y = ri, colour = "reimann"))) +
    geom_line((aes(y = tr, colour = "trapezoid"))) +
    geom_line((aes(y = si, colour = "simpsons"))) +
    ylab("integral")
```
From the plot, we can clearly see the difference between the three different methods to integrate including Riemann Integration, Trapezoid Rule, and Simpson's Rule.

