---
title: "SS4864ASS3"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SS4864ASS3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SS4864ASS3)
```
There are three useful theories in this document including: 

1.Riemann integration
2.Trapezoid Rule
3.Simpson's Rule

How to run the package:
f is a function with a single argument x
range is a vector specifying the lower and upper end points of the range of integration (a and b)
n is the number of intervals for the Riemann approximation
return a single value which is the approximation to the integral in one of the three ways above

```{r}
a <- 1
b <- 10
n <- 1000
dx <- (b - a)/n

f <- function(x){x^2}

xlist <- c()
ylist <- c()
for (x in seq(a, b-dx, dx)){
    xlist <- c(xlist, c(x, x, x + dx, x + dx))
    ylist <- c(ylist, c(0,f(x), f(x+dx), 0))
}

df <- tibble(x = xlist, y = ylist)

df %>%
    ggplot(aes(x = x, y = y)) +
    geom_line(data = tibble(x = seq(a, b, .001), 
                            y = f(x)), colour = "blue", lwd = 1) +
    geom_polygon(fill = "blue", alpha = 0.4)

```


